---
title: "Defining Marketing strategies based on company's transaction data"
output: html_document
---
 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Required libraries

```{r}
library(readr)
library(dplyr)
library(arules)
library(tidyr)
```

#### Importing Data

```{r}
data <- read_csv("transaction_history.csv")
```

#### Cleaning the data

Removing letters "C" & "A" at the beginning of InvoiceNo, as InvoiceNo contains only number and not letters:

```{r}
a=grep("^[A-Z]", data$InvoiceNo)
data$tempo=data$InvoiceNo
data$tempo[a]=substr(data$tempo[a], 2, 8)
data$InvoiceNo=data$tempo
data=data[-9]
```

Removing the negative quantities:

```{r}
data=subset(data, Quantity>=0)
```

Converting description to lower case :

```{r}
data$Description=tolower(data$Description)
```

**Note** :I keep missing CustomerID here as we need to identify the most profitable product, which is independent of the customerID

Removing discount from dataframe as they are not actual transactions:

```{r}
data=subset(data, StockCode!="D")
```

## The most popular Product:

```{r}
B=summarise(group_by(data, StockCode), Count=length(StockCode))
B=B[order(B$Count, decreasing = TRUE),]
C=summarise(group_by(data, StockCode, Description), Count=length(Description))
subset(C, C$StockCode==B$StockCode[1])
```

## The Country with highest transactions:

```{r}
B=summarise(group_by(data, Country), Count=length(InvoiceNo))
B=B[order(B$Count, decreasing = TRUE),]
B$Country[1]
```

## The most profitable Product:

```{r}
data$paid=data$Quantity*data$UnitPrice
B=summarise(group_by(data, StockCode, Description),times_perchased=length(StockCode), profitability=sum(paid))
B=B[order(B$profitability, decreasing = TRUE),]
subset(B, B$StockCode==B$StockCode[c(1,2)])[c(1,2)]
```
**Note:** 'DOT' (description = DOTCOM POSTAGE) seems to indicate the amount spent by the customer on postage. Postage isn’t a direct indicator of sales and might skew the amount spent across cohorts. So, I take the second item as the most profitable
```{r}
subset(B, B$StockCode==B$StockCode[2])[c(1,2)]
```

## The most recurrent Customer:

```{r}
B=summarise(group_by(data, CustomerID), Count=length(unique(InvoiceDate)))
B=B[order(B$Count, decreasing = TRUE),]
B=na.omit(B)
B$CustomerID[1]
```

## Association Rules

#### Cleaning the data
Removing the columns which are not necessary for this analysis
```{r}
data=data[,c(1,2)]
```
Changing StockCode column name to item
```{r}
names(data)[2]="item"
```

#### Creating transaction format data

```{r}
write.csv(data, "dataTransac.csv", row.names = F)
trans <- read.transactions(
  file = "dataTransac.csv",
  format = "single",
  sep = ",", header = T,
  cols=c("InvoiceNo","item"),
  rm.duplicates = T
)
```

#### Visualizing the 25 first items with highest frequencies (support)
```{r}
itemFrequencyPlot(trans, topN=25)
```

#### Another method of finding the most populat Product
```{r}
sort(itemFrequency(trans), decreasing = TRUE)[1]
```

### Using the association rules and the Apriori algorithm, I determine 3 rules that  are of interest to the company: 
```{r}
assoc_rules <- apriori(trans, parameter = list(supp=0.026, conf=0.8,maxlen=5))
Apriori_df = inspect(assoc_rules)
inspect(sort(assoc_rules,by="support"))
```

**Interpretation of Rule 1:**

- support: 3.05% : 3.05% of clients buy 22698(pink regency teacup and saucer) and 22697(Green regency teacup and saucer)
-	confidence = 82.6%, : 82.6% of clients who buy 22698 will also buy 22697
-	lift=16.87: The clients who buy 22698 have 16.87 times more chance to buy 22697 compared to all the clients in general.
