---
title: "Classification model"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Required libraries

```{r}
library(readr)
```

#### Importing Data

```{r}
df <- read_delim("data.csv", ";", escape_double = FALSE, trim_ws = TRUE)
```

#### Cleaning the data

Removing extra characters in column name by changing the column names:

```{r}
colnames(df)= gsub('"','',colnames(df))
```

Removing extra characters in each column values:

```{r}
df$age=gsub('"','',df$age)
df$job=gsub('"','',df$job)
df$marital=gsub('"','', df$marital)
df$education=gsub('"','',df$education)
df$default=gsub('"','', df$default)
df$housing=gsub('"','', df$housing)
df$loan=gsub('"','', df$loan)
df$contact=gsub('"','', df$contact)
df$month=gsub('"','', df$month)
df$poutcome=gsub('"','', df$poutcome)
df$y=gsub('"','', df$y)
```

Duplicate verification
```{r}
ifelse(nrow(df[(duplicated(df)) , ])==0,"No duplicate", "There are duplicated in the table")
```

Average and Median of age of the Clients accounts' balance :
```{r}
summary(df)
```
Summary result shows that age variable is character so I convert it to numeric
```{r}
df$age=as.numeric(df$age)
```

Average and Median of age of the Clients accounts' balance :
```{r}
paste("Avrage age of the clients is: ",round(mean(df$age),1), " years")
paste("Median of age of clients is: ",median(df$age), "years")
```

Changing the name of the variable representing if the client has subscribed to direct deposit or no to ‘deposit’
```{r}
names(df)[grep("^y", colnames(df))]="deposit"
```